Probabilistic Forecasts in Hierarchical~Time~Series

### 2018-07-08 ProbabilisticCoherence.tex
Some improved English in Section 4+

\documentclass[a4paper, 11pt]{article}
\usepackage{monashwp}
\usepackage{amssymb, qtree, bm, multirow, textcmds, siunitx,paralist}
\usepackage{mathrsfs, float, booktabs,todonotes,amsthm}
\usepackage[bb=boondox]{mathalfa}
\usepackage{tikz}
\usetikzlibrary{arrows,positioning,shapes,fit,calc}
\usepackage{amsfonts}
\hypersetup{citecolor=blue,linkcolor=blue,urlcolor=blue}
\DeclareNameAlias{sortname}{last-first}
\DeclareMathOperator*{\argmin}{arg\,min}
\newcolumntype{L}{>{$}l<{$}} % math-mode version of "l" column type
\def\mathbi#1{\textit{ #1}}
\def\mathB#1{\textbf{ #1}}
\def\E{\text{E}}
\mathtoolsset{showonlyrefs=true}

@@

We also cover the issue of forecast evaluation of probabilistic forecasts via scoring rules. In particular, we prove that for a coherent data generating process, the log score is not proper with respect to incoherent forecasts. As such we recommend the use of the energy score or variogram score for comparing reconciled to unreconciled forecasts. Two or more reconciled forecasts can be compared using log score, energy score or variogram score, although we show that comparisons should be made on the full hierarchy for the latter two scores.

@@

\subsection{Notation and Preliminaries}\label{sec:notation}

@@

\subsection{Coherent Point Forecasts}\label{sec:cohpointf}

@@

\begin{definition}[Coherent subspace]\label{def:cohspace}
 The $m$-dimensional linear subspace $\mathfrak{s}\subset \mathbb{R}^n$ that is spanned by the columns of $\bm{S}$, i.e. $\mathfrak{s}=\text{span}(\bm{S})$, is defined as the \emph{coherent space}.
\end{definition}

@@

\subsection{Coherent Probabilistic Forecasts}\label{sec:cohprobf}

@@

These definitions of the coherent space $\mathfrak{s}$, and coherent point and probabilistic forecasts in terms of the mapping $s(.)$, may give the impression that the bottom-level series play an important role in the definition. However, alternative definitions could be formed using any set of basis vectors that span $\mathfrak{s}$. For example, consider the most simple three variable hierarchy where $y_{1,t}=y_{2,t}+y_{3,t}$. In this case the matrix $\bm{S}$ has columns $(1,1,0)'$ and $(1,0,1)'$ spanning $\mathfrak{s}$, and premultiplying by $\bm{S}$ transforms arbitrary values of $y_{2,t}$ and $y_{3,t}$ into a coherent vector for the full hierarchy. However the columns $(1,0,1)'$ and $(0,1,-1)'$ also span $\mathfrak{s}$ and define a mapping that transforms arbitrary values of $y_{1,t}$ and $y_{2,t}$ into a coherent vector for the full hierarchy. The definitions above could be made in terms of any series and not just the bottom-level series. In general, we call the series (or linear combinations thereof) used in the definitions of coherence \textit{basis series}. Unless stated otherwise, we will always assume that the basis series are the bottom-level series as in Definition~\ref{def:cohpoint} and Definition~\ref{def:cohprob}, since this facilitates comparison with existing approaches in the literature.

@@

\begin{table}[!h]
	\caption{Summary of reconciliation methods that are projections. Here, $\hat{\bm{W}}^{sam}$ is the variance covariance matrix of one-step ahead forecast errors, $\hat{\bm{W}}^{shr}$ is a shrinkage estimator more suited to large dimensions proposed by \citet{Schafer2005}, $\hat{\bm{W}}^{wls}$ is the diagonal matrix with diagonal elements $w_{ii}$, and $\tau = \frac{\sum_{i \neq j}\hat{\text{Var}}(\hat{w}_{ij})}{\sum_{i \neq j}{\hat{w}}^2_{ij}}$, where $w_{ij}$ denotes the $(i,j)$th element of $\hat{\bm{W}}^{sam}$.}\label{table:2}
	\centering\setstretch{1.5}
	\begin{tabular}{lll}
		\toprule
		\textbf{Method} & \textbf{$\bm{W}$} & \textbf{ $\bm{R}'_\bot$}      \\
		\midrule
		OLS             &
		$\bm{I}$  &
		$\bm{S}'$  \\
		MinT(Sample)    &
		$\hat{\bm{W}}^{sam}$ &
		$\bm{S}'(\hat{\bm{W}}^{sam})^{-1}$ \\
		MinT(Shrink)    &
		$\tau\text{Diag}(\hat{\bm{W}}^{sam}) + (1-\tau)\hat{\bm{W}}^{sam}$ &
		$\bm{S}'(\hat{\bm{W}}^{shr})^{-1}$ \\
		WLS       &
		$\text{Diag}(\hat{\bm{W}}^{shr})$ &
		$\bm{S}'(\hat{\bm{W}}^{wls})^{-1}$ \\
		\bottomrule
	\end{tabular}
\end{table}

@@

The columns of $\bm{S}$ and $\bm{R}$ provide a basis for $\mathbb{R}^n$. As such, any incoherent set of point forecasts $\hat{\bm{y}}_{t+h|t} \in \mathbb{R}^n$, can be expressed in terms of coordinates in the basis defined by $\bm{S}$ and $\bm{R}$. Let $\tilde{\bm{b}}_{t+h|t}$ and $\tilde{\bm{a}}_{t+h|t}$ be the coordinates corresponding to $\bm{S}$ and $\bm{R}$ respectively, after a change of basis. The process of reconciliation involves setting the values of the reconciled bottom-level series to be $\tilde{\bm{b}}_{t+h|t}$, and setting $\tilde{\bm{a}}_{t+h}=\bm{0}$ to ensure coherence. From properties of linear algebra it follows that
%\[
%(\bm{S} ~ \vdots~ \bm{R})
%(\tilde{\bm{b}}'_{t+h},~ \tilde{\bm{t}}'_{t+h})'
%= \hat{\bm{y}}_{t+h},
%\]
\[
  \hat{\bm{y}}_{t+h|t} = (\bm{S} ~ \bm{R})
  \begin{pmatrix}
  \tilde{\bm{b}}_{t+h|t}\\ \tilde{\bm{a}}_{t+h|t}
  \end{pmatrix}= \bm{S}\tilde{\bm{b}}_{t+h|t} + \bm{R}\tilde{\bm{a}}_{t+h|t},
\]
while setting $\tilde{\bm{a}}_{t+h|t}=\bm{0}$ gives the reconciled point forecast
\[
  \tilde{\bm{y}}_{t+h|t} = \bm{S}\tilde{\bm{b}}_{t+h|t}.
\]

@@

Point reconciliation methods based on projections will always minimise the distance between unreconciled and reconciled forecasts, however the specific distance will depend on the choice of $\bm{R}$. For example OLS minimises the Euclidean distance between $\hat{\bm{y}}$ and $\tilde{\bm{y}}$, while \citet{Wickramasuriya2017} show that MinT minimises the Mahalonobis distance between $\hat{\bm{y}}$ and $\tilde{\bm{y}}$. Bottom-up methods minimise distance between reconciled and unreconciled forecasts only along dimensions corresponding to the bottom-level series. As such, bottom-up methods should be thought of as a boundary case of reconciliation methods, since they ultimately do not use information at all levels of the hierarchy.

@@

\subsection{Elliptical Distributions}

@@

In the context of probabilistic forecast reconciliation there could be two motivations for using scoring rules. The first is to compare unreconciled densities to reconciled densities. Although reconciliation is a valuable goal in and of itself since it can be important in aligning decision making across, for example, different units of an enterprise, in the point forecasting literature, forecast reconciliation has also been shown to improve forecast performance \citep{AthEtAl2017, Wickramasuriya2017}. It will be worthwhile to see whether the same holds in the probabilistic forecasting case. The second motivation for using scoring rules is to compare two or more sets of reconciled probabilistic forecasts to one another. The objective here is to evaluate which reconciliation mapping $g(.)$ works best in practice.

\subsection{Univariate Scoring rules}

One way to evaluate probabilistic forecasts is via the application of univariate scoring rules to each variable in a hierarchy. A summary can be taken of the expected scores across each margin for example a mean or median. In the simulations of section~\ref{sec:gaussian} we consider two scoring rules. The log score is given by the log density, in this case for each margin of the probabilistic forecast. The cumulative rank probability score generalises mean square error and is given by
\begin{align} \label{eq:CRPS}
\text{CRPS}(\breve{F}_i,y_{i}) &=\int \left(\breve{F}_i(\breve{Y}_i)-\mathbb{1}(y_i<y_{i})\right)d\breve{Y}_i\\ &=\E_{\breve{Y}_i}|\breve{Y}_{i}-y_{i}| - \frac{1}{2}\E_{\breve{Y}_i}|\breve{Y}_{i}-\breve{Y}^*_{i}|\,,
\end{align}
where $\breve{F}_i$ is the cumulative distribution function of the $i^{th}$ margin of the probabilistic forecast, $\breve{Y}_i$ and $\breve{Y}^*_{T+h,i}$ are independent copies of a random variable with distribution $\breve{F}_i$ and $y_i$ is the outcome of the $i^{th}$ margin. The expectations in the second line can be approximated by Monte Carlo when a sample from the predictive distribution is available.

An advantage to this approach is that it allows the forecaster to evaluate the levels and individual series of the hierarchy where the gains from reconciliation are greatest. For this reason this approach has been used in the limited literature on probabilistic forecasting for hierarchies \citep{BenTaieb2017, JeoEtAl2018} to date. A major shortcomings of this approach however, is that evaluating univariate scores on the margins do not account for the dependence in the hierarchy.

\subsection{Multivariate Scoring rules}

@@

The log score can be approximated using a sample of values from the probabilistic forecast density \citep{Jordan2017} however it is more commonly used when a parametric form for the density is available for the probabilistic forecast. The energy score on the other hand can be defined in terms of the characteristic function of the probabilistic forecast, but the representation in terms of expectations leads itself to easy computation when samples from the probabilistic forecast are available.
An interesting limiting case is where $\alpha=2$, where it can be easily shown that
\begin{equation} \label{eq:(5.1)}
\text{ES}(\breve{\bm{Y}_{T+h},y_{T+h}}) = \|\bm{y}_{T+h}-\breve{\bm{\mu}}_{T+h}\|^2,
\end{equation}
where $\breve{\bm{\mu}}_{T+h} =\E_{\bm{F}}(\breve{\bm{Y}}_{T+h}) $. In this limiting case, the energy score only measures the accuracy of the forecast mean, and not the entire distribution and the energy score is proper, but not strictly proper. \citet{Pinson2013a} also argues that the energy score has low discriminative ability for incorrectly specified covariances, even though it discriminates the misspecified means well.

In contrast, \citet{SCHEUERER2015} have shown that the variogram score has a higher discrimination ability of misspecified means, variances and correlation structures than the energy score. When $\breve{\bm{y}}$ is a random variable from probabilistic forecast $\breve{F}$, the empirical variogram score is defined as
\begin{equation}
\text{VS}(\breve{F}, \bm{y}) = \displaystyle\sum_{i=1}^{n}\displaystyle\sum_{j=1}^{n}w_{ij}\left(|y_{i} - y_{j}|^p - E_{\breve{Y}_i,\breve{Y}_j} |\breve{Y}^k_{i}-\breve{Y}^k_{j}|^p\right)^2.
\end{equation}
\citet{SCHEUERER2015} recommend using $p=0.5$.

@@

\subsubsection{Comparing Unreconciled Forecasts to Reconciled Forecasts}

For both reconciled and unreconciled densities it is possible to obtain a density from the probability measures defined in \ref{sec:definitions}. As such it may seem sensible to compare unreconciled densities to reconciled densities on the basis of log score. The following theorem shows that using the log score may fail in the case of multivariate distributions with a degeneracy.

\begin{theo}[Impropriety of log score]
	When the true data generating process is coherent, then the log score is improper with respect to the class of incoherent measures.
\end{theo}
\begin{proof}
Consider a rotated version of hierarchical time series $\bm{z}_t=\bm{U}\bm{y}_t$ so that the first $m$ elements of $\bm{z}_t$ denoted $\bm{z}^{(1)}_t$ are unconstrained, while the remaining $n-m$ elements denoted $\bm{z}^{(2)}_t$ equal $0$ when the aggregation constraints hold. An example of the $n\times n$ $\bm{U}$ could be the matrix of left singular vectors of $\bm{S}$. %For a non-degenerate probability measure on $\mathbb{R}^n$, the density is the Radon-Nikodym derivative with respect to the usual Lesbegue measure on $\mathbb{R}^n$. %For a coherent probability measure the density after rotation is the Radon-Nikodym derivative with respect to the usual Lesbegue measure on $\mathbb{R}^m$.

Consider the case where the true predictive density is $f_1(\bm{z}^{(1)}_t)\mathbb{1}\left(\bm{z}^{(2)}_t=\bm{0}\right)$, and we evaluate an incoherent density is given by $f_1(\bm{z}^{(1)}_t)f_2(\bm{z}^{(2)}_t)$, where $f_2$ is highly concentrated around $0$ but still a non-degenerate. For example $f_2$ may be Gaussian with variance $\sigma^2{\bm{I}}$ with $\sigma^2 < (2\pi)^{-1}$. The log score under the true data generating process is
\[
S\left(\tilde{f},\bm{z}^{(1)}_t\right) = -\log f_1\left(\bm{z}^{(1)}_t\right),
\]
while that of the unreconciled density is
\begin{align}
S\left(\hat{f},\bm{z}^{(1)}_t\right) &= -\log f_1(\bm{z}^{(1)}_t)-f_2(\bm{z}^{(1)}_t)\\
&= -\log f_1(\bm{z}^{(1)}_t)+\frac{n-m}{2}\log(2\pi\sigma^2)\\
&<-\log f_1(\bm{z}^{(1)}_t).
\end{align}

After taking expectations $ES(f,f) > ES(\hat{f},f)$, violating the condition in Equation~\eqref{eq:(3.1.)} for a proper scoring rule.
\end{proof}

A similar issue also arises when discrete random variables are modelled as if they were continuous, an issue discussed in Section 4.1 of \citet{Gneiting2007}. This implies that the log score should be avoided when comparing reconciled and unreconciled probabilistic forecasts.

\subsubsection{Comparing Reconciled Forecasts to one another}

Coherent probabilistic forecasts can be completely characterised in terms of basis series; if a probabilistic forecast is  available for the basis series then a probabilistic forecast can be recovered for  the  entire hierarchy via Definition~\ref{def:cohprob}. This may suggest that it is adequate to merely compare two coherent forecasts to  one  another using  the basis series only. We now show how this  depends on the specific scoring rule used.

For the log score, suppose the coherent probabilistic forecast has density $f(\bm{b})$. The density for the full hierarchy is given by $f(\bm{y})=f(\bm{Sb})=f(\bm{b})J^{-1}$ where $J=\prod_{j=1}^{m}\lambda_j$ is a pseudo-determinant of the non-square  matrix $\bm{S}$ and $\lambda_j$ are the non-zero singular values of $\bm{S}$. Therefore for any coherent density the log score of the full hierarchy differs from the log score for the bottom-level series by the term $log(J)$. This term depends  only on the structure of the  hierarchy and is fixed across different reconciliation methods. Therefore if one method achieves a lower expected log score compared to an alternative method  using the bottom-level series only, the same ordering is preserved when an assessment is made on the basis of the full hierarchy.

The same property does not hold for all scores in general. For example, energy score can be expressed in terms of expectations of norms. In general, since norms are invariant under orthogonal rotations the energy score is also invariant under orthogonal transformations \citep{Szekely2013,Gneiting2007}. In the context of two coherent forecasts the same is true of a semi-orthogonal transformation from a lower dimensional basis series to the full hierarchy. However,  when $\bm{S}$ is  the usual summing matrix, it is not semi-orthogonal. As such the energy score computed on the bottom-level series will differ from the energy score computed using the full hierarchy and the ordering of different reconciliation methods may change depending on the basis series used. In this case we recommend computing energy score using the full hierarchy. Although the discussion here is related to energy score, the same logic holds for other multivariate scores that are not invariant to orthogonal rotations, for example the variogram score.

@@

\begin{table}
	\centering
	\begin{tabular}{rll}
	& Coherent v Incoherent &Coherent v Coherent\\
	\hline
	Log Score & Not proper & Ordering preserved if compared using\\ &&bottom level only\\
	Energy/ & Proper & Full hierarchy should be used\\
	Variogram Score & &\\
	\hline
    \end{tabular}
	\caption{Summary of properties of scoring rules in the context of reconciled probabilistic forecasts.}
	\label{tab:prop}

\end{table}

@@

\section{Simulation Study}\label{sec:gaussian}

@@

We now turn our attention to comparing different reconciliation methods in a simulation study where the data is conditionally Gaussian. We choose the Gaussian case due to its analytical tractability which allows for evaluation using all scoring rules (including the log score). The non-Gaussian case lies beyond the scope of this simulation study, but can be handled by a bootstrapping approach proposed in separate work.

@@

Tables~\ref{table:4} and~\ref{table:5} break down the forecasting performance of different reconciliation methods by considering univariate scores on each individual margin. The log score and CRPS are considered while skill scores are computed with the unreconciled forecast as a reference. When broken down in this fashion, the methods based on MinT perform best for all series and always outperform bottom-up and unreconciled forecasts.

\begin{table}
	\caption{Comparison of coherent forecasts. ``Energy score'' and ``Variogram score'' columns give scores based on the joint forecast distribution of whole hierarchy. ``Log score'' column gives the log scores of the joint forecast distribution of bottom level. ``Skill score'' columns give the percentage skill score with reference to the bottom-up method. Entries in these columns show the percentage increase of score for different reconciliation methods relative to the bottom-up method.}\label{table:3}

@@

By redefining coherent forecasts and forecast reconciliation in geometric terms we have established two new theoretical results that support the use of projections for point forecast reconciliation, and crucially have extended these concepts to probabilistic forecasting. We show that for elliptical distributions, the true predictive density can be recovered by linear reconciliation and establish conditions for when this linear mapping is a projection. Although this optimal projection cannot feasibly be obtained in practice, a projection similar to the MinT procedure provides a good approximation in practice. This is supported by the results of a simulation study. Finally, we also discuss strategies for evaluating probabilistic forecasts for hierarchical time series establishing a key results regarding the impropriety of the log score with respect to incoherent forecasts.

>>>>

\documentclass[a4paper, 11pt]{article}
\usepackage{monashwp}
\usepackage{amssymb, qtree, bm, multirow, textcmds, siunitx,paralist}
\usepackage{mathrsfs, float, booktabs,todonotes,amsthm}
\usepackage[bb=boondox]{mathalfa}
\usepackage{tikz}
\usetikzlibrary{arrows,positioning,shapes,fit,calc}
\usepackage{amsfonts}
\hypersetup{citecolor=blue,linkcolor=blue,urlcolor=blue}
\DeclareNameAlias{sortname}{last-first}
\DeclareMathOperator*{\argmin}{arg\,min}
\newcolumntype{L}{>{$}l<{$}} % math-mode version of "l" column type
\def\mathbi#1{\textit{ #1}}
\def\mathB#1{\textbf{ #1}}
\def\E{\text{E}}
\def\var{\text{Var}}
\mathtoolsset{showonlyrefs=true}

@@

We also cover the issue of forecast evaluation of probabilistic forecasts via scoring rules. In particular, we prove that for a coherent data generating process, the log score is not proper with respect to incoherent forecasts. Therefore we recommend the use of the energy score or variogram score for comparing reconciled to unreconciled forecasts. Two or more reconciled forecasts can be compared using log score, energy score or variogram score, although we show that comparisons should be made on the full hierarchy for the latter two scores.

@@

\subsection{Notation and preliminaries}\label{sec:notation}

@@

\subsection{Coherent point forecasts}\label{sec:cohpointf}

@@

\begin{definition}[Coherent subspace]\label{def:cohspace}
 The $m$-dimensional linear subspace $\mathfrak{s}\subset \mathbb{R}^n$ that is spanned by the columns of $\bm{S}$, i.e.\ $\mathfrak{s}=\text{span}(\bm{S})$, is defined as the \emph{coherent space}.
\end{definition}

@@

\subsection{Coherent probabilistic forecasts}\label{sec:cohprobf}

@@

These definitions of the coherent space $\mathfrak{s}$, and coherent point and probabilistic forecasts in terms of the mapping $s(.)$, may give the impression that the bottom-level series play an important role in the definition. However, alternative definitions could be formed using any set of basis vectors that span $\mathfrak{s}$. For example, consider the most simple three variable hierarchy where $y_{1,t}=y_{2,t}+y_{3,t}$. In this case the matrix $\bm{S}$ has columns $(1,1,0)'$ and $(1,0,1)'$ spanning $\mathfrak{s}$, and pre-multiplying by $\bm{S}$ transforms arbitrary values of $y_{2,t}$ and $y_{3,t}$ into a coherent vector for the full hierarchy. However the columns $(1,0,1)'$ and $(0,1,-1)'$ also span $\mathfrak{s}$ and define a mapping that transforms arbitrary values of $y_{1,t}$ and $y_{2,t}$ into a coherent vector for the full hierarchy. The definitions above could be made in terms of any series and not just the bottom-level series. In general, we call the series (or linear combinations thereof) used in the definitions of coherence \textit{basis series}. Unless stated otherwise, we will always assume that the basis series are the bottom-level series as in Definition~\ref{def:cohpoint} and Definition~\ref{def:cohprob}, since this facilitates comparison with existing approaches in the literature.

@@

\begin{table}[!h]
	\caption{Summary of reconciliation methods that are projections. Here, $\hat{\bm{W}}^{sam}$ is the variance covariance matrix of one-step ahead forecast errors, $\hat{\bm{W}}^{shr}$ is a shrinkage estimator more suited to large dimensions proposed by \citet{Schafer2005}, $\hat{\bm{W}}^{wls}$ is the diagonal matrix with diagonal elements $w_{ii}$, and $\tau = \frac{\sum_{i \neq j}\hat{\var}(\hat{w}_{ij})}{\sum_{i \neq j}{\hat{w}}^2_{ij}}$, where $w_{ij}$ denotes the $(i,j)$th element of $\hat{\bm{W}}^{sam}$.}\label{table:2}
	\centering\setstretch{1.5}
	\begin{tabular}{lll}
		\toprule
		\textbf{Method} & \textbf{$\bm{W}$} & \textbf{ $\bm{R}'_\bot$}      \\
		\midrule
		OLS             &
		$\bm{I}$  &
		$\bm{S}'$  \\
		MinT(Sample)    &
		$\hat{\bm{W}}^{sam}$ &
		$\bm{S}'(\hat{\bm{W}}^{sam})^{-1}$ \\
		MinT(Shrink)    &
		$\tau\text{Diag}(\hat{\bm{W}}^{sam}) + (1-\tau)\hat{\bm{W}}^{sam}$ &
		$\bm{S}'(\hat{\bm{W}}^{shr})^{-1}$ \\
		WLS       &
		$\text{Diag}(\hat{\bm{W}}^{shr})$ &
		$\bm{S}'(\hat{\bm{W}}^{wls})^{-1}$ \\
		\bottomrule
	\end{tabular}
\end{table}

@@

The columns of $\bm{S}$ and $\bm{R}$ provide a basis for $\mathbb{R}^n$. Therefore any incoherent set of point forecasts $\hat{\bm{y}}_{t+h|t} \in \mathbb{R}^n$ can be expressed in terms of coordinates in the basis defined by $\bm{S}$ and $\bm{R}$. Let $\tilde{\bm{b}}_{t+h|t}$ and $\tilde{\bm{a}}_{t+h|t}$ be the coordinates corresponding to $\bm{S}$ and $\bm{R}$ respectively, after a change of basis. The process of reconciliation involves setting the values of the reconciled bottom-level series to be $\tilde{\bm{b}}_{t+h|t}$, and setting $\tilde{\bm{a}}_{t+h}=\bm{0}$ to ensure coherence. From properties of linear algebra it follows that
%\[
%(\bm{S} ~ \vdots~ \bm{R})
%(\tilde{\bm{b}}'_{t+h},~ \tilde{\bm{t}}'_{t+h})'
%= \hat{\bm{y}}_{t+h},
%\]
\[
  \hat{\bm{y}}_{t+h|t} = (\bm{S} ~ \bm{R})
  \begin{pmatrix}
  \tilde{\bm{b}}_{t+h|t}\\ \tilde{\bm{a}}_{t+h|t}
  \end{pmatrix}= \bm{S}\tilde{\bm{b}}_{t+h|t} + \bm{R}\tilde{\bm{a}}_{t+h|t},
\]
while setting $\tilde{\bm{a}}_{t+h|t}=\bm{0}$ gives the reconciled point forecast
\[
  \tilde{\bm{y}}_{t+h|t} = \bm{S}\tilde{\bm{b}}_{t+h|t}.
\]

@@

Point reconciliation methods based on projections will always minimise the distance between unreconciled and reconciled forecasts, however the specific distance will depend on the choice of $\bm{R}$. For example OLS minimises the Euclidean distance between $\hat{\bm{y}}$ and $\tilde{\bm{y}}$, while \citet{Wickramasuriya2017} show that MinT minimises the Mahalonobis distance between $\hat{\bm{y}}$ and $\tilde{\bm{y}}$. Bottom-up methods minimise distance between reconciled and unreconciled forecasts only along dimensions corresponding to the bottom-level series. Therefore bottom-up methods should be thought of as a boundary case of reconciliation methods, since they ultimately do not use information at all levels of the hierarchy.

@@

\subsection{Elliptical distributions}

@@

In the context of probabilistic forecast reconciliation there could be two motivations for using scoring rules. The first is to compare unreconciled densities to reconciled densities. Reconciliation itself is a valuable goal since it can be important in aligning decision making across, for example, different units of an enterprise. In the point forecasting literature, forecast reconciliation has also been shown to improve forecast performance \citep{AthEtAl2017, Wickramasuriya2017}. It will be worthwhile to see whether the same holds in the probabilistic forecasting case. The second motivation for using scoring rules is to compare two or more sets of reconciled probabilistic forecasts to one another. The objective here is to evaluate which reconciliation mapping $g(.)$ works best in practice.

\subsection{Univariate scoring rules}

One way to evaluate hierarchical probabilistic forecasts is via the application of univariate scoring rules to each variable in the hierarchy. A summary can be taken of the expected scores across each margin, for example a mean or median. In the simulations of Section~\ref{sec:gaussian}, we consider two scoring rules. The log score is given by the log density, in this case for each margin of the probabilistic forecast. The cumulative rank probability score generalises mean square error and is given by
\begin{align} \label{eq:CRPS}
\text{CRPS}(\breve{F}_i,y_{i}) &=\int \left(\breve{F}_i(\breve{Y}_i)-\mathbb{1}(y_i<y_{i})\right)d\breve{Y}_i\\ &=\E_{\breve{Y}_i}|\breve{Y}_{i}-y_{i}| - \frac{1}{2}\E_{\breve{Y}_i}|\breve{Y}_{i}-\breve{Y}^*_{i}|\,,
\end{align}
where $\breve{F}_i$ is the cumulative distribution function of the $i$th margin of the probabilistic forecast, $\breve{Y}_i$ and $\breve{Y}^*_{T+h,i}$ are independent copies of a random variable with distribution $\breve{F}_i$, and $y_i$ is the outcome of the $i$th margin. The expectations in the second line can be approximated by Monte Carlo when a sample from the predictive distribution is available.

An advantage to this approach is that it allows the forecaster to evaluate the levels and individual series of the hierarchy where the gains from reconciliation are greatest. For this reason this approach has been used in the limited literature on probabilistic forecasting for hierarchies \citep{BenTaieb2017, JeoEtAl2018} to date. A major shortcoming of this approach however, is that evaluating univariate scores on the margins does not account for the dependence in the hierarchy.

\subsection{Multivariate scoring rules}

@@

The log score can be approximated using a sample of values from the probabilistic forecast density \citep{Jordan2017}; however it is more commonly used when a parametric form for the density is available for the probabilistic forecast.

The energy score on the other hand can be defined in terms of the characteristic function of the probabilistic forecast, but the representation in terms of expectations leads itself to easy computation when samples from the probabilistic forecast are available. An interesting limiting case is where $\alpha=2$, where it can be easily shown that
\begin{equation} \label{eq:(5.1)}
\text{ES}(\breve{\bm{Y}_{T+h},y_{T+h}}) = \|\bm{y}_{T+h}-\breve{\bm{\mu}}_{T+h}\|^2,
\end{equation}
where $\breve{\bm{\mu}}_{T+h} =\E_{\bm{F}}(\breve{\bm{Y}}_{T+h}) $. In this limiting case, the energy score only measures the accuracy of the forecast mean (not the entire distribution), and the energy score is proper but not strictly proper. \citet{Pinson2013a} also argue that the energy score has low discriminative ability for incorrectly specified covariances, even though it discriminates the misspecified means well.

In contrast, \citet{SCHEUERER2015} have shown that the variogram score has a higher discrimination ability for misspecified means, variances and correlation structures than the energy score. When $\breve{\bm{y}}$ is a random variable from probabilistic forecast $\breve{F}$, the empirical variogram score is defined as
\begin{equation}
\text{VS}(\breve{F}, \bm{y}) = \displaystyle\sum_{i=1}^{n}\displaystyle\sum_{j=1}^{n}w_{ij}\left(|y_{i} - y_{j}|^p - E_{\breve{Y}_i,\breve{Y}_j} |\breve{Y}^k_{i}-\breve{Y}^k_{j}|^p\right)^2.
\end{equation}
\citet{SCHEUERER2015} recommend using $p=0.5$.

@@

\subsubsection{Comparing unreconciled forecasts to reconciled forecasts}

For both reconciled and unreconciled densities it is possible to obtain a density from the probability measures defined in Section~\ref{sec:definitions}. Therefore it may seem sensible to compare unreconciled densities to reconciled densities on the basis of log score. However, the following theorem shows that using the log score may fail in the case of multivariate distributions with a degeneracy.

\begin{theo}[Impropriety of log score]
	When the true data generating process is coherent, then the log score is improper with respect to the class of incoherent measures.
\end{theo}

\begin{proof}
Consider a rotated version of hierarchical time series, $\bm{z}_t=\bm{U}\bm{y}_t$, so that the first $m$ elements of $\bm{z}_t$ denoted $\bm{z}^{(1)}_t$ are unconstrained, while the remaining $n-m$ elements denoted $\bm{z}^{(2)}_t$ equal $0$ when the aggregation constraints hold. An example of the $n\times n$ $\bm{U}$ is the matrix of left singular vectors of $\bm{S}$. %For a non-degenerate probability measure on $\mathbb{R}^n$, the density is the Radon-Nikodym derivative with respect to the usual Lesbegue measure on $\mathbb{R}^n$. %For a coherent probability measure the density after rotation is the Radon-Nikodym derivative with respect to the usual Lesbegue measure on $\mathbb{R}^m$.

Consider the case where the true predictive density is $f_1(\bm{z}^{(1)}_t)\mathbb{1}\left(\bm{z}^{(2)}_t=\bm{0}\right)$, and we evaluate an incoherent density given by $f_1(\bm{z}^{(1)}_t)f_2(\bm{z}^{(2)}_t)$, where $f_2$ is highly concentrated around $0$ but still non-degenerate. For example, $f_2$ may be Gaussian with variance $\sigma^2{\bm{I}}$ with $\sigma^2 < (2\pi)^{-1}$. The log score under the true data generating process is
\[
S\left(\tilde{f},\bm{z}^{(1)}_t\right) = -\log f_1\left(\bm{z}^{(1)}_t\right),
\]
while that of the unreconciled density is
\begin{align}
S\left(\hat{f},\bm{z}^{(1)}_t\right) &= -\log f_1(\bm{z}^{(1)}_t)-f_2(\bm{z}^{(1)}_t)\\
&= -\log f_1(\bm{z}^{(1)}_t)+\frac{n-m}{2}\log(2\pi\sigma^2)\\
&<-\log f_1(\bm{z}^{(1)}_t).
\end{align}
After taking expectations $ES(f,f) > ES(\hat{f},f)$, violating the condition in Equation~\eqref{eq:(3.1.)} for a proper scoring rule.
\end{proof}

A similar issue also arises when discrete random variables are modelled as if they were continuous, an issue discussed in Section~4.1 of \citet{Gneiting2007}. This implies that the log score should be avoided when comparing reconciled and unreconciled probabilistic forecasts.

\subsubsection{Comparing reconciled forecasts to one another}

Coherent probabilistic forecasts can be completely characterised in terms of basis series; if a probabilistic forecast is available for the basis series, then a probabilistic forecast can be recovered for the entire hierarchy via Definition~\ref{def:cohprob}. This may suggest that it is adequate to merely compare two coherent forecasts to one another using the basis series only. We now show how this depends on the specific scoring rule used.

For the log score, suppose the coherent probabilistic forecast has density $f(\bm{b})$. The density for the full hierarchy is given by $f(\bm{y})=f(\bm{Sb})=f(\bm{b})J^{-1}$, where $J=\prod_{j=1}^{m}\lambda_j$ is a pseudo-determinant of the non-square matrix $\bm{S}$ and $\lambda_j$ are the non-zero singular values of $\bm{S}$. Therefore for any coherent density, the log score of the full hierarchy differs from the log score for the bottom-level series by the term $log(J)$. This term depends only on the structure of the hierarchy and is fixed across different reconciliation methods. Therefore if one method achieves a lower expected log score compared to an alternative method using the bottom-level series only, the same ordering is preserved when an assessment is made on the basis of the full hierarchy.

The same property does not hold for all scores in general. For example, the energy score can be expressed in terms of expectations of norms. In general, since norms are invariant under orthogonal rotations, the energy score is also invariant under orthogonal transformations \citep{Szekely2013,Gneiting2007}. In the context of two coherent forecasts, the same is true of a semi-orthogonal transformation from a lower dimensional basis series to the full hierarchy. However, when $\bm{S}$ is the usual summing matrix, it is not semi-orthogonal. Therefore the energy score computed on the bottom-level series will differ from the energy score computed using the full hierarchy and the ordering of different reconciliation methods may change depending on the basis series used. In this case we recommend computing the energy score using the full hierarchy. Although the discussion here is related to energy score, the same logic holds for other multivariate scores that are not invariant to orthogonal rotations, for example the variogram score.

@@

\begin{table}
	\centering
	\begin{tabular}{rll}
	& Coherent v Incoherent &Coherent v Coherent\\
	\hline
	Log Score & Not proper & Ordering preserved if compared using\\ &&bottom level only\\
	Energy/ & Proper & Full hierarchy should be used\\
	Variogram Score & &\\
	\hline
    \end{tabular}
	\caption{Summary of properties of scoring rules in the context of reconciled probabilistic forecasts.}
	\label{tab:prop}
\end{table}

@@

\section{Simulation study}\label{sec:gaussian}

@@

We now turn our attention to comparing different reconciliation methods in a simulation study where the data is conditionally Gaussian. We choose the Gaussian case due to its analytical tractability which allows for evaluation using all scoring rules (including the log score). The non-Gaussian case lies beyond the scope of this simulation study.

@@

Tables~\ref{table:4} and~\ref{table:5} break down the forecasting performance of different reconciliation methods by considering univariate scores on each individual margin. The log score and CRPS are considered, while skill scores are computed with the unreconciled forecast as a reference. When broken down in this fashion, the methods based on MinT perform best for all series and always outperform bottom-up and unreconciled forecasts.

\begin{table}
	\caption{Comparison of coherent forecasts. ``Energy score'' and ``Variogram score'' columns give scores based on the joint forecast distribution of the whole hierarchy. ``Log score'' column gives the log scores of the joint forecast distribution of the bottom level. ``Skill score'' columns give the percentage skill score with reference to the bottom-up method. Entries in these columns show the percentage increase of scores for different reconciliation methods relative to the bottom-up method.}\label{table:3}

@@

By redefining coherent forecasts and forecast reconciliation in geometric terms, we have established two new theoretical results that support the use of projections for point forecast reconciliation, and have allowed us to extend these concepts to probabilistic forecasting. We have shown that for elliptical distributions the true predictive density can be recovered by linear reconciliation and we have established conditions for when this linear mapping is a projection. Although this optimal projection cannot feasibly be obtained in practice, a projection similar to the MinT procedure provides a good approximation in applications. This is supported by the results of a simulation study. Finally, we have also discussed strategies for evaluating probabilistic forecasts for hierarchical time series, establishing a key result regarding the impropriety of the log score with respect to incoherent forecasts.
